Study of the hadronization of charged pions

### 2016-10-20 AnalysisNote.tex
Changes from Lamiaa

\begin{abstract}
Hadronization is the process by which energetic quarks transform into 
colorless hadrons. The process is non-perturbative, therefore, only 
qualitative understanding can be achieved, and using phenomenological models 
is necessary. By comparing hadron production 
on different nuclei, one can measure variables with different sensitivities 
to the hadronization phases, the two principal variables are: the transverse 
momentum broadening, that is believed to be tightly connected to quark energy 
loss and the multiplicity ratio, which is a measure of the hadron attenuation 
in the medium.

The goals of the experiment E-02-104 are to study both quark propagation
and hadronization dynamics using various nuclear target.
In this analysis we focus on two particles, the positive and negative pions
to constrain theoritical models using a precise multidimensional analysis.

>>>>

\begin{abstract}
Hadronization is the process by which energetic quarks transform into colorless hadrons. The process is non-perturbative, therefore, only a qualitative understanding based on phenomenological models can be achieved. By comparing hadron production on different nuclei, one can measure the most sensitive variables to the hadronization phases, the transverse momentum broadening, that is believed to be tightly connected to the quark energy loss, and the multiplicity ratio, which is a measure of the hadron attenuation in the nuclear medium.

The goal of the experiment E-02-104 was the study of the quark propagation and hadronization dynamics using various nuclear targets. In this note, we focus on the production of two charged particles, positive and negative pions, to constrain theoretical models using a precise multidimensional analysis.
